Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2014-10-16 draft_lm1.tex
fixed bugs in the model; it is still not parameterized correctly...

\section*{Introduction}
When modeling infecctious disease spread using dynamic models, the initial 
conditions of the system, although key to match the simulated dynamics to 
observed data, are frequently overlooked.

@@

Determining the viral types in circulation during an epidemic is 
expensive, as it requires virus isolatio and reverse-transcriptase-PCR. 
Therefore only a very limited number of samples are examined on any epidemic. 
Besides, mild cases are rarely detected let alone tested for dengue.

>>>>

\section*{Introduction}

@@

Determining the viral types in circulation during an epidemic is 
expensive, as it requires virus isolation and reverse-transcriptase-PCR. 
Therefore only a very limited number of samples are examined on any epidemic. 
Besides, mild cases are rarely detected let alone tested for dengue.
